Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)

### 2025-08-23 analysis/paper/paper.qmd
update

# Kruskal–Wallis test
# on sphericity among 4 clusters

@@

# Elbow method for optimal K
wss <- numeric(10)

for (k in 1:10) {
  set.seed(123)  
  km <- kmeans(umap_data[, c("x", "y")], centers = k)
  wss[k] <- km$tot.withinss  
}

elbow_test <-
  plot(1:10, wss, type="b", pch=19, frame=FALSE,
       xlab="Number of clusters K",
       ylab="Total within-cluster sum of squares (WSS)",
       main="Elbow Method for Optimal K")

>>>>

# Kruskal–Wallis test
# on sphericity among clusters

@@

# Elbow method for optimal K
#wss <- numeric(10)

#for (k in 1:10) {
  #set.seed(123)  
  #km <- kmeans(umap_data[, c("x", "y")], centers = k)
  #wss[k] <- km$tot.withinss  }

#elbow_test <-
  #plot(1:10, wss, type="b", pch=19, frame=FALSE,
       #xlab="Number of clusters K",
       #ylab="Total within-cluster sum of squares (WSS)",
       #main="Elbow Method for Optimal K")
